Bayesian beta regressions with brms in R: A tutorial for phoneticians

### 2025-02-11 manuscript/manuscript.qmd
clear cache and rerender
fix typos

library(tidyverse)
library(brms)
library(collapse)
library(marginaleffects)
```

@@

The output of Bayesian regression models is (posterior) probability distributions for the model parameters, through which researchers can quantify (un)certainty. Bayesian Credible Intervals (CrIs) can be calculated from the posterior distributions at several probability levels (e.g. 95, 90, 80, 60%) for a more complete view on estimated parameters. Bayesian CrIs indicate that at a certain probability levels the parameter's estimate lies within that interval: so, for example, a 90% CrI \[A, B\] indicates that there is a 90% probability that the estimate is between A and B. Different probability levels correspond to different levels of confidence: the higher the probability the higher the confidence (always conditional on data and model). Readers interested in a full and accessible exposition of Bayesian statistics are referred to @mcelreath2019. Shorter introductions can be found in @etz2018, @vasishth2018 and @nalborczyk2019.

@@

@fig-ita-egg shows the raw voicing duration proportion values split by vowel /i, e, a, o, u/ and second consonant /k, t, p/ in the /CVCo/ target words. The plot suggests that, on average, the voicing proportion is slightly lower with /k/ than with /t, p/. Moreover, there is greater variability between vowels in /t, p/ than in /k/. We will use a beta regression model to assess whether the place of articulation of the consonant affects the proportion of coarticulatory progressive voicing, while averaging across vowels (of course, another question that could be answered with the same model is if different vowels lead to difference voicing proportions, but for sake of space we restrict this tutorial to the former question). A general expectation is that the proportion of progressive voicing should increase with fronter places of articulation (so from /k/ to /t/ to /p/) given the aerodynamic constraints which obtain with vocal fold vibration during a fully occluded oral tract [@vandenberg1958; @rothenberg1967; @ohala2011].

@@

The `summary()` function prints the full model summary. For conciseness, we will use the `fixef()` function which prints the regression coefficients. The full summary with an explanation of each part can be found in XXX. @tbl-voi-prop-fixef reports the output of `fixef()` as a table (we round all values to the nearest 2 digits for clarity.). For each coefficient in the model, `fixef()` prints the name of the coefficient, the mean estimate, the estimate error and the lower and upper limits of a Bayesian Credible interval (CrI). Note that all values are in log-odds, since the link function in beta regressions is the logistic function, like in binomial/Bernoulli regressions. Here, we print an 80% CrI. There is nothing special about 95% CrI within Bayesian inference and instead experts recommend to check and report a variety of CrIs. Obtaining CrIs at different probability levels allows researchers to make more fine-grained inferential statements than the frequentist significance dichotomy affords. For simplicity of exposition, we will use 80% CrIs in this case study but we strongly recommend researchers to always obtain CrIs at different levels of probability and base their inferences on all and not one in particular. To reiterate, in Bayesian inference, an 80% CrI indicates the range of values within which the true estimate falls at 80% probability or confidence.

@@

Before being able to plot the predictions, it's important to get familiar with the so-called posterior draws. Bayesian regression models are fitted using Markov Chain Monte Carlo (MCMC) methods, as briefly explained in @sec-bayes. The `brm()` function runs three MCMC chains with 2000 iterations each by default. These are sufficient in most cases. The first 1000 iterations of each chain are used for "warmup", where the MCMC algorithm is optimised to find the posterior probability. The second half of the iterations, 1000 per chain, are used for sampling from the posterior probability. Each iteration returns a drawn value for each parameter in the model. The list of values drawn during the Monte Carlo sampling are called the "posterior draws". The posterior draws are used for inference: we can plot them, summarise them, transform them and combine them in any way to answer specific questions.

Posterior draws can be conveniently obtained with the `as_draws_df()` from brms. For the moment, we will extract only the draws of the constant regression coefficients (model variables starting with `b_`). To check which coefficients are available in a model, use `get_variables()` from the tidybayes package [@kay2019]. `as_draws_df()` returns a tibble where each column contains the drawn values of a coefficient. @tbl-voi-prop-draws shows the first ten rows and first five columns of the output of `as_draws_df()`. The probability distribution of the drawn values of each coefficient is the posterior probability distribution of that coefficient. Note that, due to the indexing coding of vowel and C2, all coefficient except `b_speech_rate_c` are *predicted log-odds* for each vowel/C2 combination (the drawn values for `b_speech_rate_c` are drawn *differences* in log-odds for each unit increase of speech rate). The drawn values are in log-odds, but we can convert them to proportions with `plogis()` (we will do this when plotting below).

```{r}
#| label: voi-prop-bm-draws

@@

What if we want to plot the average predicted voicing proportion for the three consonants /k, t, p/? One approach is to take the mean across vowels within each consonant for each posterior draw, and the posterior distribution of the resulting list of values is the predicted posterior distribution of voicing proportion for each consonant, assuming an "average" vowel.

@@

Based on the model and data, there is a 90% probability that the voicing proportion in /p/ is 1.07-1.38 times longer (or 7-38% increase) than in /t, k/. At 80% confidence, the change ratio is 1.10-1.34 (or 10-34% increase) while at 60% confidence is 1.14-1.30 (14-30% increase). In other words we can be quite confident that the voicing proportion in /p/ is longer than in /t, k/ and that the increase is less than 35%. The brms package comes with a convenient function, `conditional_effects()`, to plot posterior means and CrIs based on predictors in the model. In @fig-voi-prop-bm-cond, we plot the predicted proportion of voicing by consonant and vowel.

@@

Finally, the package marginaleffects [@arelbundock2025] has two other convenience functions that return CrIs of comparisons across predictor levels (`avg_comparisons()`) and CrIs of posterior predictions across predictor levels (`avg_predictions`). Both functions take the model and a list of variables as arguments. Optionally, you can set the confidence level with the `conf_level` argument (here, we set it to 0.8, or 80%). `avg_comparisons()` allows the user to specify the type of comparison for each variable: here we set `"pairwise"` to calculate pairwise comparisons of each level of `c2`. The output of the two functions is shows in @tbl-marginal-1 and @tbl-marginal-2.

@@

Moving onto question 2: is there individual speaker variation? While in the recent tradition of linguistic research to use varying (aka random) effects to *control* for differences across participants, it has been proposed to use the estimates of the varying coefficients to investigate individual differences [@tamminga2016]. We will use the `spread_draws()` function from tidybayes [@kay2019] to extract the draws of the varying terms (in brms these are the coefficients that start with `r_`). There is quite a few steps of processing to get from the raw draws to the estimand we need: while we have commented the following code, we encourage readers to test each line sequentially and inspect the intermediate output to fully understand the process. We assume that readers are familiar enough with models with varying terms (aka random effects, mixed-effects models). What readers should note is that to obtain the expected predictions of nasalisation proportion for each speaker, the constant terms and the varying terms should be added (since the varying terms indicate the deviation of each speaker from the overall estimate).

>>>>

library(tidyverse)
theme_set(theme_light())
library(brms)
library(collapse)
library(marginaleffects)
library(posterior)
```

@@

The output of Bayesian regression models is (posterior) probability distributions for the model parameters, through which researchers can quantify (un)certainty. Bayesian Credible Intervals (CrIs) can be calculated from the posterior distributions at several probability levels (e.g. 95, 90, 80, 60%) for a more complete view on estimated parameters. Bayesian CrIs indicate that, at a certain probability level, the parameter's estimate lies within that interval: so, for example, a 90% CrI \[A, B\] indicates that there is a 90% probability that the estimate is between A and B. Different probability levels correspond to different levels of confidence: the higher the probability the higher the confidence (always conditional on data and model). Readers interested in a full and accessible exposition of Bayesian statistics are referred to @mcelreath2019. Shorter introductions can be found in @etz2018, @vasishth2018 and @nalborczyk2019.

@@

@fig-ita-egg shows the raw voicing duration proportion values split by vowel /i, e, a, o, u/ and second consonant /k, t, p/ in the /CVCo/ target words. The plot suggests that, on average, the voicing proportion is slightly lower with /k/ than with /t, p/. Moreover, there is greater variability between vowels in /t, p/ than in /k/. We will use a beta regression model to assess whether the place of articulation of the consonant affects the proportion of coarticulatory progressive voicing, while averaging across vowels (of course, another question that could be answered with the same model is if different vowels lead to different voicing proportions, but for sake of space we restrict this tutorial to the former question). A general expectation is that the proportion of progressive voicing should increase with fronter places of articulation (so from /k/ to /t/ to /p/) given the aerodynamic constraints which obtain with vocal fold vibration during a fully occluded oral tract [@vandenberg1958; @rothenberg1967; @ohala2011].

@@

The `summary()` function prints the full model summary. For conciseness, we will use the `fixef()` function which prints the regression coefficients. @tbl-voi-prop-fixef reports the output of `fixef()` as a table (we round all values to the nearest 2 digits for clarity.). For each coefficient in the model, `fixef()` prints the name of the coefficient, the mean estimate, the estimate error and the lower and upper limits of a Bayesian Credible interval (CrI). Note that all values are in log-odds, since the link function in beta regressions is the logistic function, like in binomial/Bernoulli regressions. Here, we print an 80% CrI. There is nothing special about 95% CrI within Bayesian inference and instead experts recommend to check and report a variety of CrIs. Obtaining CrIs at different probability levels allows researchers to make more fine-grained inferential statements than the frequentist significance dichotomy affords. For simplicity of exposition, we will use 80% CrIs in this case study but we strongly recommend researchers to always obtain CrIs at different levels of probability and base their inferences on all and not one in particular. To reiterate, in Bayesian inference, an 80% CrI indicates the range of values within which the true estimate falls at 80% probability or confidence.

@@

Before being able to plot the predictions, it's important to get familiar with the so-called posterior draws. Bayesian regression models are fitted using Markov Chain Monte Carlo (MCMC) methods, as briefly explained in @sec-bayes. The `brm()` function runs four MCMC chains with 2000 iterations each by default. These are sufficient in most cases. The first 1000 iterations of each chain are used for "warmup", where the MCMC algorithm is optimised to find the posterior probability. The second half of the iterations, 1000 per chain, are used for sampling from the posterior probability. Each iteration returns a drawn value for each parameter in the model. The list of values drawn during the Monte Carlo sampling are called the "posterior draws". Since four chains are run, a total of 4000 posterior values are generated. The posterior draws are used for inference: we can plot them, summarise them, transform them and combine them in any way to answer specific questions.

Posterior draws can be conveniently obtained with the `as_draws_df()` from brms. For the moment, we will extract only the draws of the constant (aka fixed) regression coefficients (model variables starting with `b_`). To check which coefficients are available in a model, use `get_variables()` from the tidybayes package [@kay2019]. `as_draws_df()` returns a tibble where each column contains the drawn values of a coefficient. @tbl-voi-prop-draws shows the first ten rows and first five columns of the output of `as_draws_df()`. The probability distribution of the drawn values of each coefficient is the posterior probability distribution of that coefficient. Note that, due to the indexing coding of vowel and C2, all coefficient except `b_speech_rate_c` are drawn *log-odds values* for each vowel/C2 combination (the drawn values for `b_speech_rate_c` are drawn *differences* in log-odds values for each unit increase of speech rate). The drawn values are in log-odds, but we can convert them to proportions with `plogis()` (we will do this when plotting below).

```{r}
#| label: voi-prop-bm-draws
#| warning: false

@@

What if we want to plot the average predicted voicing proportion for the three consonants /k, t, p/? One approach is to take the mean across vowels within each consonant for each posterior draw, and the posterior distribution of the resulting list of values is the predicted posterior distribution of voicing proportion for each consonant, assuming an "average" vowel. See @fig-voi-pbdl-c2.

@@

Based on the model and data, there is a 90% probability that the voicing proportion in /p/ is 1.07-1.38 times longer (or 7-38% increase) than in /t, k/. At 80% confidence, the change ratio is 1.10-1.34 (or 10-34% increase) while at 60% confidence is 1.14-1.30 (14-30% increase). In other words we can be quite confident that the voicing proportion in /p/ is greater than in /t, k/ and that the increase is less than 35%. The brms package comes with a convenient function, `conditional_effects()`, to plot posterior means and CrIs based on predictors in the model. In @fig-voi-prop-bm-cond, we plot the predicted proportion of voicing by consonant and vowel.

@@

Finally, the package marginaleffects [@arelbundock2025] has two other convenience functions that return CrIs of comparisons across predictor levels (`avg_comparisons()`) and CrIs of posterior predictions across predictor levels (`avg_predictions`). Both functions take the model and a list of variables as arguments. Optionally, you can set the confidence level with the `conf_level` argument (here, we set it to 0.8, or 80%). `avg_comparisons()` allows the user to specify the type of comparison for each variable: here we set `"pairwise"` to calculate pairwise comparisons of each level of `c2`. The output of the two functions is shown in @tbl-marginal-1 and @tbl-marginal-2.

@@

Moving onto question 2: is there individual speaker variation? While in the recent tradition of linguistic research, varying (aka random) effects are used to *control* for differences across participants, it has been proposed to use the estimates of the varying coefficients to investigate individual differences [@tamminga2016]. We will use the `spread_draws()` function from tidybayes [@kay2019] to extract the draws of the varying terms (in brms these are the coefficients that start with `r_`). There is quite a few steps of processing to get from the raw draws to the estimand we need: while we have commented the following code, we encourage readers to test each line sequentially and inspect the intermediate output to fully understand the process. We assume that readers are familiar enough with models with varying terms (aka random effects, mixed-effects, hierarchical, multilevel, nested models). What readers should note is that to obtain the expected predictions of nasalisation proportion for each speaker, the constant terms and the varying terms should be added (since the varying terms indicate the deviation of each speaker from the overall estimate).

### 2025-02-11 manuscript/manuscript.tex
fix typos

The output of Bayesian regression models is (posterior) probability
distributions for the model parameters, through which researchers can
quantify (un)certainty. Bayesian Credible Intervals (CrIs) can be
calculated from the posterior distributions at several probability
levels (e.g.~95, 90, 80, 60\%) for a more complete view on estimated
parameters. Bayesian CrIs indicate that at a certain probability levels
the parameter's estimate lies within that interval: so, for example, a
90\% CrI {[}A, B{]} indicates that there is a 90\% probability that the
estimate is between A and B. Different probability levels correspond to
different levels of confidence: the higher the probability the higher
the confidence (always conditional on data and model). Readers
interested in a full and accessible exposition of Bayesian statistics
are referred to \citet{mcelreath2019}. Shorter introductions can be
found in \citet{etz2018}, \citet{vasishth2018} and
\citet{nalborczyk2019}.

@@

Figure~\ref{fig-ita-egg} shows the raw voicing duration proportion
values split by vowel /i, e, a, o, u/ and second consonant /k, t, p/ in
the /CVCo/ target words. The plot suggests that, on average, the voicing
proportion is slightly lower with /k/ than with /t, p/. Moreover, there
is greater variability between vowels in /t, p/ than in /k/. We will use
a beta regression model to assess whether the place of articulation of
the consonant affects the proportion of coarticulatory progressive
voicing, while averaging across vowels (of course, another question that
could be answered with the same model is if different vowels lead to
difference voicing proportions, but for sake of space we restrict this
tutorial to the former question). A general expectation is that the
proportion of progressive voicing should increase with fronter places of
articulation (so from /k/ to /t/ to /p/) given the aerodynamic
constraints which obtain with vocal fold vibration during a fully
occluded oral tract \citep{vandenberg1958, rothenberg1967, ohala2011}.

@@

The \texttt{summary()} function prints the full model summary. For
conciseness, we will use the \texttt{fixef()} function which prints the
regression coefficients. The full summary with an explanation of each
part can be found in XXX. Table~\ref{tbl-voi-prop-fixef} reports the
output of \texttt{fixef()} as a table (we round all values to the
nearest 2 digits for clarity.). For each coefficient in the model,
\texttt{fixef()} prints the name of the coefficient, the mean estimate,
the estimate error and the lower and upper limits of a Bayesian Credible
interval (CrI). Note that all values are in log-odds, since the link
function in beta regressions is the logistic function, like in
binomial/Bernoulli regressions. Here, we print an 80\% CrI. There is
nothing special about 95\% CrI within Bayesian inference and instead
experts recommend to check and report a variety of CrIs. Obtaining CrIs
at different probability levels allows researchers to make more
fine-grained inferential statements than the frequentist significance
dichotomy affords. For simplicity of exposition, we will use 80\% CrIs
in this case study but we strongly recommend researchers to always
obtain CrIs at different levels of probability and base their inferences
on all and not one in particular. To reiterate, in Bayesian inference,
an 80\% CrI indicates the range of values within which the true estimate
falls at 80\% probability or confidence.

@@

Before being able to plot the predictions, it's important to get
familiar with the so-called posterior draws. Bayesian regression models
are fitted using Markov Chain Monte Carlo (MCMC) methods, as briefly
explained in Section~\ref{sec-bayes}. The \texttt{brm()} function runs
three MCMC chains with 2000 iterations each by default. These are
sufficient in most cases. The first 1000 iterations of each chain are
used for ``warmup'', where the MCMC algorithm is optimised to find the
posterior probability. The second half of the iterations, 1000 per
chain, are used for sampling from the posterior probability. Each
iteration returns a drawn value for each parameter in the model. The
list of values drawn during the Monte Carlo sampling are called the
``posterior draws''. The posterior draws are used for inference: we can
plot them, summarise them, transform them and combine them in any way to
answer specific questions.

Posterior draws can be conveniently obtained with the
\texttt{as\_draws\_df()} from brms. For the moment, we will extract only
the draws of the constant regression coefficients (model variables
starting with \texttt{b\_}). To check which coefficients are available
in a model, use \texttt{get\_variables()} from the tidybayes package
\citep{kay2019}. \texttt{as\_draws\_df()} returns a tibble where each
column contains the drawn values of a coefficient.
Table~\ref{tbl-voi-prop-draws} shows the first ten rows and first five
columns of the output of \texttt{as\_draws\_df()}. The probability
distribution of the drawn values of each coefficient is the posterior
probability distribution of that coefficient. Note that, due to the
indexing coding of vowel and C2, all coefficient except
\texttt{b\_speech\_rate\_c} are \emph{predicted log-odds} for each
vowel/C2 combination (the drawn values for \texttt{b\_speech\_rate\_c}
are drawn \emph{differences} in log-odds for each unit increase of
speech rate). The drawn values are in log-odds, but we can convert them
to proportions with \texttt{plogis()} (we will do this when plotting
below).

@@

What if we want to plot the average predicted voicing proportion for the
three consonants /k, t, p/? One approach is to take the mean across
vowels within each consonant for each posterior draw, and the posterior
distribution of the resulting list of values is the predicted posterior
distribution of voicing proportion for each consonant, assuming an
``average'' vowel.

@@

Based on the model and data, there is a 90\% probability that the
voicing proportion in /p/ is 1.07-1.38 times longer (or 7-38\% increase)
than in /t, k/. At 80\% confidence, the change ratio is 1.10-1.34 (or
10-34\% increase) while at 60\% confidence is 1.14-1.30 (14-30\%
increase). In other words we can be quite confident that the voicing
proportion in /p/ is longer than in /t, k/ and that the increase is less
than 35\%. The brms package comes with a convenient function,
\texttt{conditional\_effects()}, to plot posterior means and CrIs based
on predictors in the model. In Figure~\ref{fig-voi-prop-bm-cond}, we
plot the predicted proportion of voicing by consonant and vowel.

@@

Finally, the package marginaleffects \citep{arelbundock2025} has two
other convenience functions that return CrIs of comparisons across
predictor levels (\texttt{avg\_comparisons()}) and CrIs of posterior
predictions across predictor levels (\texttt{avg\_predictions}). Both
functions take the model and a list of variables as arguments.
Optionally, you can set the confidence level with the
\texttt{conf\_level} argument (here, we set it to 0.8, or 80\%).
\texttt{avg\_comparisons()} allows the user to specify the type of
comparison for each variable: here we set \texttt{"pairwise"} to
calculate pairwise comparisons of each level of \texttt{c2}. The output
of the two functions is shows in Table~\ref{tbl-marginal-1} and
Table~\ref{tbl-marginal-2}.

@@

Moving onto question 2: is there individual speaker variation? While in
the recent tradition of linguistic research to use varying (aka random)
effects to \emph{control} for differences across participants, it has
been proposed to use the estimates of the varying coefficients to
investigate individual differences \citep{tamminga2016}. We will use the
\texttt{spread\_draws()} function from tidybayes \citep{kay2019} to
extract the draws of the varying terms (in brms these are the
coefficients that start with \texttt{r\_}). There is quite a few steps
of processing to get from the raw draws to the estimand we need: while
we have commented the following code, we encourage readers to test each
line sequentially and inspect the intermediate output to fully
understand the process. We assume that readers are familiar enough with
models with varying terms (aka random effects, mixed-effects models).
What readers should note is that to obtain the expected predictions of
nasalisation proportion for each speaker, the constant terms and the
varying terms should be added (since the varying terms indicate the
deviation of each speaker from the overall estimate).

>>>>

The output of Bayesian regression models is (posterior) probability
distributions for the model parameters, through which researchers can
quantify (un)certainty. Bayesian Credible Intervals (CrIs) can be
calculated from the posterior distributions at several probability
levels (e.g.~95, 90, 80, 60\%) for a more complete view on estimated
parameters. Bayesian CrIs indicate that, at a certain probability level,
the parameter's estimate lies within that interval: so, for example, a
90\% CrI {[}A, B{]} indicates that there is a 90\% probability that the
estimate is between A and B. Different probability levels correspond to
different levels of confidence: the higher the probability the higher
the confidence (always conditional on data and model). Readers
interested in a full and accessible exposition of Bayesian statistics
are referred to \citet{mcelreath2019}. Shorter introductions can be
found in \citet{etz2018}, \citet{vasishth2018} and
\citet{nalborczyk2019}.

@@

Figure~\ref{fig-ita-egg} shows the raw voicing duration proportion
values split by vowel /i, e, a, o, u/ and second consonant /k, t, p/ in
the /CVCo/ target words. The plot suggests that, on average, the voicing
proportion is slightly lower with /k/ than with /t, p/. Moreover, there
is greater variability between vowels in /t, p/ than in /k/. We will use
a beta regression model to assess whether the place of articulation of
the consonant affects the proportion of coarticulatory progressive
voicing, while averaging across vowels (of course, another question that
could be answered with the same model is if different vowels lead to
different voicing proportions, but for sake of space we restrict this
tutorial to the former question). A general expectation is that the
proportion of progressive voicing should increase with fronter places of
articulation (so from /k/ to /t/ to /p/) given the aerodynamic
constraints which obtain with vocal fold vibration during a fully
occluded oral tract \citep{vandenberg1958, rothenberg1967, ohala2011}.

@@

The \texttt{summary()} function prints the full model summary. For
conciseness, we will use the \texttt{fixef()} function which prints the
regression coefficients. Table~\ref{tbl-voi-prop-fixef} reports the
output of \texttt{fixef()} as a table (we round all values to the
nearest 2 digits for clarity.). For each coefficient in the model,
\texttt{fixef()} prints the name of the coefficient, the mean estimate,
the estimate error and the lower and upper limits of a Bayesian Credible
interval (CrI). Note that all values are in log-odds, since the link
function in beta regressions is the logistic function, like in
binomial/Bernoulli regressions. Here, we print an 80\% CrI. There is
nothing special about 95\% CrI within Bayesian inference and instead
experts recommend to check and report a variety of CrIs. Obtaining CrIs
at different probability levels allows researchers to make more
fine-grained inferential statements than the frequentist significance
dichotomy affords. For simplicity of exposition, we will use 80\% CrIs
in this case study but we strongly recommend researchers to always
obtain CrIs at different levels of probability and base their inferences
on all and not one in particular. To reiterate, in Bayesian inference,
an 80\% CrI indicates the range of values within which the true estimate
falls at 80\% probability or confidence.

@@

Before being able to plot the predictions, it's important to get
familiar with the so-called posterior draws. Bayesian regression models
are fitted using Markov Chain Monte Carlo (MCMC) methods, as briefly
explained in Section~\ref{sec-bayes}. The \texttt{brm()} function runs
four MCMC chains with 2000 iterations each by default. These are
sufficient in most cases. The first 1000 iterations of each chain are
used for ``warmup'', where the MCMC algorithm is optimised to find the
posterior probability. The second half of the iterations, 1000 per
chain, are used for sampling from the posterior probability. Each
iteration returns a drawn value for each parameter in the model. The
list of values drawn during the Monte Carlo sampling are called the
``posterior draws''. Since four chains are run, a total of 4000
posterior values are generated. The posterior draws are used for
inference: we can plot them, summarise them, transform them and combine
them in any way to answer specific questions.

Posterior draws can be conveniently obtained with the
\texttt{as\_draws\_df()} from brms. For the moment, we will extract only
the draws of the constant (aka fixed) regression coefficients (model
variables starting with \texttt{b\_}). To check which coefficients are
available in a model, use \texttt{get\_variables()} from the tidybayes
package \citep{kay2019}. \texttt{as\_draws\_df()} returns a tibble where
each column contains the drawn values of a coefficient.
Table~\ref{tbl-voi-prop-draws} shows the first ten rows and first five
columns of the output of \texttt{as\_draws\_df()}. The probability
distribution of the drawn values of each coefficient is the posterior
probability distribution of that coefficient. Note that, due to the
indexing coding of vowel and C2, all coefficient except
\texttt{b\_speech\_rate\_c} are drawn \emph{log-odds values} for each
vowel/C2 combination (the drawn values for \texttt{b\_speech\_rate\_c}
are drawn \emph{differences} in log-odds values for each unit increase
of speech rate). The drawn values are in log-odds, but we can convert
them to proportions with \texttt{plogis()} (we will do this when
plotting below).

@@

What if we want to plot the average predicted voicing proportion for the
three consonants /k, t, p/? One approach is to take the mean across
vowels within each consonant for each posterior draw, and the posterior
distribution of the resulting list of values is the predicted posterior
distribution of voicing proportion for each consonant, assuming an
``average'' vowel. See Figure~\ref{fig-voi-pbdl-c2}.

@@

Based on the model and data, there is a 90\% probability that the
voicing proportion in /p/ is 1.07-1.38 times longer (or 7-38\% increase)
than in /t, k/. At 80\% confidence, the change ratio is 1.10-1.34 (or
10-34\% increase) while at 60\% confidence is 1.14-1.30 (14-30\%
increase). In other words we can be quite confident that the voicing
proportion in /p/ is greater than in /t, k/ and that the increase is
less than 35\%. The brms package comes with a convenient function,
\texttt{conditional\_effects()}, to plot posterior means and CrIs based
on predictors in the model. In Figure~\ref{fig-voi-prop-bm-cond}, we
plot the predicted proportion of voicing by consonant and vowel.

@@

Finally, the package marginaleffects \citep{arelbundock2025} has two
other convenience functions that return CrIs of comparisons across
predictor levels (\texttt{avg\_comparisons()}) and CrIs of posterior
predictions across predictor levels (\texttt{avg\_predictions}). Both
functions take the model and a list of variables as arguments.
Optionally, you can set the confidence level with the
\texttt{conf\_level} argument (here, we set it to 0.8, or 80\%).
\texttt{avg\_comparisons()} allows the user to specify the type of
comparison for each variable: here we set \texttt{"pairwise"} to
calculate pairwise comparisons of each level of \texttt{c2}. The output
of the two functions is shown in Table~\ref{tbl-marginal-1} and
Table~\ref{tbl-marginal-2}.

@@

Moving onto question 2: is there individual speaker variation? While in
the recent tradition of linguistic research, varying (aka random)
effects are used to \emph{control} for differences across participants,
it has been proposed to use the estimates of the varying coefficients to
investigate individual differences \citep{tamminga2016}. We will use the
\texttt{spread\_draws()} function from tidybayes \citep{kay2019} to
extract the draws of the varying terms (in brms these are the
coefficients that start with \texttt{r\_}). There is quite a few steps
of processing to get from the raw draws to the estimand we need: while
we have commented the following code, we encourage readers to test each
line sequentially and inspect the intermediate output to fully
understand the process. We assume that readers are familiar enough with
models with varying terms (aka random effects, mixed-effects,
hierarchical, multilevel, nested models). What readers should note is
that to obtain the expected predictions of nasalisation proportion for
each speaker, the constant terms and the varying terms should be added
(since the varying terms indicate the deviation of each speaker from the
overall estimate).
